Faithful Variable Screening for High-Dimensional Convex Regression

### 2014-07-24 tex/scam/appendix.tex
bracketing number results

Intuitively, we would like to show the following:
\begin{align*}
\| f_0 - \hat{f} \|_P & \approx \| f_0 - f^* \|_P \\
\| f_0 - f^* - \hat{g}_k \|_P & \approx \| f_0 - f^* - g^*_k \|_P 
       \quad \trm{for all $k \in S$ where $f^*_k = 0$}
\end{align*}
where the difference is a term that decreases with $n$.

@@

\begin{theorem}
\label{thm:convex_consistent}
Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq c sLb\sqrt{ \frac{1}{n} \log^2 np}$.

Then, with probability at least $1-\delta$,
\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
&\leq c (Lb)^3\sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{np}{\delta}}
\end{align}

@@

The middle term can be bounded with the fact that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 4Lb$ because $f^*_k$ as is $L$-Lipschitz and supported on $[-b, b]$.

\begin{align*}
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* + \bar{f}^* \|_n^2 
   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s L b 
\end{align*}

Using Lemma~\ref{lem:remove_centering}, we can remove $\bar{f}^*$ from the LHS. With probability at least $1 - \delta$:
\begin{align}
\label{eqn:first_step_inequality}
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s L b + c(sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
\end{align}

[TOOD: at this point, we still have to choose a value for $\lambda$]\\

@@

\textbf{Step 2.} We upper bound $2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle$ with theorem~\ref{thm:chaining}.\\

Define $\mathcal{G}$ as $\{ f - f^* + \bar{f}^* \,:\, f \in \mathcal{C}^s_L\}$ as the set of convex additive functions centered around the function $f^* - \bar{f}^*$.

@@

Plugging this result into equation~\ref{eqn:first_step_inequality} and using an union bound, we get, with probability at least $1 - 2\delta$:
\begin{align}
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq c (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
   + \lambda 4 s L b + c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq c (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
   + \lambda 4 s L b    \label{eqn:second_step_inequality}
\end{align}

@@

\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
   &\leq c (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
 +\lambda 4 s L b + c (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
    \nonumber \\
&\leq c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}} + \lambda 4 sLb
\end{align}

Substituting in $\lambda \leq c sLb \sqrt{\frac{1}{n} \log^2 np}$ and we get the desired result.

@@

\begin{proof}
The proof proceeds almost identically to that of theorem~\ref{thm:convex_consistent} because convex and concave functions have the same covering number.

@@

Using the chaining result (theorem~\ref{thm:chaining}), setting $s=1$, we have, with probability at least $1-\delta$,
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
  c (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb
\end{align*}

@@

\begin{lemma}
\label{lem:uniform_convergence}
With probability at least $1-\delta$:
\begin{align*}
\sup_{f \in \mathcal{C}^s_L} \Big| \| f_0 - f \|^2_n - \|f_0 - f \|^2_P\Big| \leq
   c (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
\end{align*}

@@

\begin{proof}
Let $\mathcal{G}$ denote the off-centered set of convex functions, that is, $\mathcal{G} \equiv \mathcal{C}^s_L - f_0$. Note that if $h \in \mathcal{G}$, then $\| h \|_\infty = \| f_0 - f \|_\infty \leq 4 s b L$.\\

By Corollary~\ref{cor:convexbracket_ln}, there exists a bracketing $\mathcal{G}_\epsilon$ of $\mathcal{G}$ which has sized bounded by [TODO:...], which is an $\epsilon$-bracketing with respect to the $L_2(P)$ norm, and which is also an $(\epsilon + \epsilon_{n,\delta})$-bracketing with respect to the $L_n$ norm with probability at least $1-\delta$.

For a $h \in \mathcal{G}$, let $h_\epsilon$ denote a function in the $\epsilon$-bracketing of $\mathcal{G}$ closest to $h$. It obviously must be that $\| h - h_\epsilon \|_n \leq \| h - h_\epsilon \|_\infty \leq \epsilon$.\\

Because $\| h \|_n = \| h - h_\epsilon + h_\epsilon \|_n$, we have that
\begin{align*}
\|h_\epsilon \|_n - \| h - h_\epsilon \|_n &\leq 
    \| h \|_n \leq \|h_\epsilon \|_n + \| h - h_\epsilon \|_n \\
\|h_\epsilon \|_n - \epsilon &\leq 
    \| h \|_n \leq \|h_\epsilon \|_n + \epsilon  \\
\| h_\epsilon \|^2_n - 8 \epsilon (s L b)  &\leq \| h  \|^2_n  \leq
   \| h_\epsilon \|_n^2 + 8 \epsilon (s L b) 
\end{align*}
where we used the fact that $\| h - h_\epsilon \|_n \leq \| h - h_\epsilon \|_\infty \leq \epsilon$ and $ \| h_\epsilon \|_n \leq \| h_\epsilon \|_\infty \leq 4 s L b$.

And likewise:
\begin{align*}
\| h_\epsilon \|^2_P - 8 \epsilon (s L b)  &\leq \| h  \|^2_P \leq
   \| h_\epsilon \|_P^2 + 8 \epsilon (s L b)
\end{align*}

Therefore, 
\begin{align*}
\sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| \leq 
\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
        + \epsilon (16 sLb)
\end{align*}

Since $\| h_\epsilon \|_n^2 = \frac{1}{n} \sum_{i=1}^n h_\epsilon(X_i)^2$ is an average of bounded random variables, we have by Union Bound and Hoeffding Inequality that, with probability at most $1 - \delta$,
\begin{align*}
\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
  (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
        + \log N_\infty(\epsilon, \mathcal{C}_L^s) \big) } \\
&\leq (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
        + C s^{1.5} Lb \epsilon^{-1/2}   \big) }
\end{align*}

We will set $\epsilon = \frac{1}{n^{2/5}} (C s^{0.5} L b)^2$. 
Therefore:
\begin{align*}
\sup_{h_\epsilon} \Big|  \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
   (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
        + s n^{1/5}  \big) } \\
  &\leq (8Lb)^2 \sqrt{ \frac{s^5}{cn^{4/5}} \log \frac{2}{\delta} }
\end{align*}
And
\begin{align*}
\sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| &\leq 
\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
        + \frac{1}{n^{2/5}} C^2 s^2 (Lb)^3 \\
  &\leq (8Lb)^2 \sqrt{ \frac{s^5}{c n^{4/5}} \log \frac{2}{\delta}}
     + (CLb)^2 \sqrt{ \frac{s^4}{n^{4/5}} } \\
  &\leq c (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
\end{align*}

@@

\begin{definition}
% upper, lower, epsilon room
% metric
% function space
Let $\mathcal{C}$ be a set of functions. For a given $\epsilon$ and metric $\rho$ (which we take to be $L_2$ or $L_2(P)$), we define a \textbf{bracketing} of $\mathcal{C}$ to be a set of pairs of functions $\{ (f^L, f^U) \}$ satisfying (1) $\rho( f^L, f^U) \leq \epsilon$ and (2) for any $f \in \mathcal{C}$, there exist a pair $(f^L, f^U)$ where $f^U \geq f \geq f^L$.

@@

It is trivial to extend Kim and Samworth's result to $L_2(P)$ norm for a distribution $P$ with an uniformly upper bounded density.

\begin{corollary}
\label{cor:convexbracket_lp}
Let $P$ be a distribution with a density $p$ upper bounded by $c_u$. Let $\mathcal{C}, b, B, \epsilon_3, K^{**}$ be defined as in Proposition~\ref{prop:convexbracket}. Then,
\[
\log N_{[]} (2\epsilon, \mathcal{C}, L_2(P)) \leq K^{**} \left( \frac{2bB c_u}{\epsilon} \right)^{d/2}
\]
\end{corollary}

Given samples $X_1,..., X_n \in \R^p$, we define $L_n$-norm as $\| f \|^2_n \equiv \frac{1}{n}\sum_{i=1}^n f(X_i)^2$. The following result follows from Corollary~\ref{cor:convexbracket_lp} directly by an union bound.

\begin{corollary}
\label{cor:convexbracket_ln}
Let $X_1,...,X_n$ be random samples from a distribution $P$. Let $1 > \delta > 0$. Let $\mathcal{C}_\epsilon$ be an $\epsilon$-bracketing of $\mathcal{C}$ with respect to the $L_2(P)$-norm whose size is at most $N_{[]}( 2\epsilon, \mathcal{C}, L_2(P))$. \\

Then, with probability at least $1-\delta$, for all pairs $(f^L, f^U) \in \mathcal{C}_\epsilon$, $\frac{1}{n} \sum_{i=1}^n ( f^L(X_i) - f^U(X_i)^2 \leq \epsilon + \epsilon_{n, \delta}$, where 
$\epsilon_{n,\delta} \equiv 
B^2 \sqrt{ \frac{ \log N_{[]}(2\epsilon, \mathcal{C}, L_2(P)) + \log \frac{1}{\delta}}{2n}} = 
B^2 \sqrt{ \frac{K^{**} (2bBc_u)^{d/2} + \log \frac{1}{\delta}}{2\epsilon^{d/2} n} }$
\end{corollary}

\begin{proof}
$(f^L(X_i) - f^U(X_i))^2$ is at most $B^2$. There are $N_{[]}(2\epsilon, \mathcal{C}, L_2(P))$ pairs $(f^L, f^U)$. The corollary follows from a direct application of union bound and Hoeffding Inequality.
\end{proof}

% \subsubsection{Covering Number for Lipschitz Convex Functions}

>>>>

Intuitively, we would like to show the following:
\begin{align*}
\| f_0 - \hat{f} \|_P & \approx \| f_0 - f^* \|_P \\
\| f_0 - f^* - \hat{g}_k \|_P & \approx \| f_0 - f^* - g^*_k \|_P 
       \quad \trm{for all $k \in S$ where $f^*_k = 0$}
\end{align*}
where the estimation error is a term that decreases with $n$.

@@

\begin{theorem}
\label{thm:convex_consistent}
Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq c sB \sqrt{ \frac{1}{n} \log^2 np}$.

Then, with probability at least $1-\delta$,
\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
&\leq c B^3\sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{np}{\delta}}
\end{align}

@@

The middle term can be bounded with the fact that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 4B$ because $f^*_k$ as is $L$-Lipschitz and supported on $[-b, b]$.

\begin{align*}
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* + \bar{f}^* \|_n^2 
   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s B 
\end{align*}

Using Lemma~\ref{lem:remove_centering}, we can remove $\bar{f}^*$ from the LHS. With probability at least $1 - \delta$:
\begin{align}
\label{eqn:first_step_inequality}
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s B + c(sB)^2 \frac{1}{n} \log \frac{2}{\delta}
\end{align}

%[TOOD: at this point, we still have to choose a value for $\lambda$]\\

@@

\textbf{Step 2.} We upper bound $2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle$ with bracketing entropy.

Define $\mathcal{G}$ as $\{ f - f^* + \bar{f}^* \,:\, f \in \mathcal{C}^s\}$ as the set of convex additive functions centered around the function $f^* - \bar{f}^*$.

By Corollary~\ref{prop:convexbracket_lp}, there is an $\epsilon$-bracketing of $\mathcal{G}$ whose size is bounded by $\log N_{[]}( 2\epsilon, \mathcal{G}, L_2(P)) \leq sK^{**} \left( \frac{2sbB}{\epsilon} \right)^{1/2}$, for all $\epsilon \in (0, sB \epsilon_3]$.

By Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h^U, h^L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$, 
$\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq 2 \epsilon + sB \sqrt{ \frac{sK^{**}(2sbB
)^{1/2} + \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$.

For each $h \in \mathcal{G}$, there exists a pair $(h_U, h_L)$ such that $h_U(X_i) - h_L(X_i) \geq h(X_i) - h_L(X_i) \geq 0$. Therefore, with probability at least $1-\delta$, uniformly for all $h \in \mathcal{G}$:

$$
\frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq \frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \leq 2\epsilon +  (sB) \sqrt{ \frac{sK^{**}(2sbBc_u)^{1/2} + \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}
$$.

We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{ \frac{sK^{**}(2sbBc_u)^{1/2} + \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. 
Therefore,  
\[
|\langle w, h - h_L\rangle_n| \leq \| w \|_\infty \frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq
  \sigma \sqrt{\log \frac{n}{\delta}} \left( \epsilon + \epsilon_{n,\delta} \right)
\]
For the last inequality, we used the fact that $w$ is a vector of independent subgaussian($\sigma$) random variables and hence, by union bound, with probability at least $1-\delta$, $\| w \|_\infty \leq \sigma \sqrt{\log \frac{n}{\delta}}$.

By another property of subgaussian random variables, with probability at least $1-\delta$, $|\langle w, h_L \rangle_n | \leq \| h_L \|_n \sigma \sqrt{ \frac{1}{cn} \log \frac{1}{\delta} }$. Applying an union bound, we have that 
$\sup_{h_L} |\langle w, h_L \rangle| \leq sB \sigma \sqrt{ \frac{\log N_{[]}}{n} \log \frac{1}{\delta}}$.

Putting this together, we have that
\begin{align*}
|\langle w, h \rangle_n | &\leq | \langle w, h_L\rangle_n| + |\langle w, h - h_L\rangle_n|\\
|\sup_{h \in \mathcal{G}} \langle w, h \rangle_n| &\leq 
     | \sup_{h^L} \langle w, h^L \rangle_n | + \sigma \sqrt{\log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
   &\leq   sB \sigma \sqrt{ \frac{ \log N_{[]} + \log 1/\delta}{cn}} + \sigma \sqrt{\log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
   &\leq  sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}}} +
   \sigma \sqrt{ \log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
   &\leq sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}}} +
   \sigma\sqrt{\log \frac{n}{\delta}} \epsilon + sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}} \log \frac{n}{\delta}} \\
   &\leq \sigma\sqrt{\log \frac{n}{\delta}} \epsilon + sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}} \log \frac{n}{\delta}} \\
\end{align*}

The two terms are balanced when one sets $\epsilon = \sqrt{ \frac{((sB)^2 s K^{**} (sBb)^{1/2})^{4/5}}{n^{4/5}} }$.

This is only valid if $n$ is large enough so that $\epsilon \in (0, sB \epsilon_3]$.

We upper bound some terms to simplify the presentations again and end up with the following result:

\[
|\sup_{h \in \mathcal{G}} \langle w, h \rangle | \leq sB \sigma \sqrt{ 
   \frac{s b^{1/2} \log \frac{1}{\delta}}{c n^{4/5}}}
\]

@@

Plugging this result into equation~\ref{eqn:first_step_inequality} and using an union bound, we get, with probability at least $1 - 2\delta$:
\begin{align}
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq c sB \sigma \sqrt{ 
   \frac{s b^{1/2} \log \frac{1}{\delta}}{c n^{4/5}}}
   + \lambda 4 s B + c (sB)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq sB \sigma \sqrt{ 
   \frac{s b^{1/2} \log \frac{1}{\delta}}{c n^{4/5}}}
   + \lambda 4 s B \nonumber\\   
   &\leq cB \sigma 
    \sqrt{ \frac{s^3 b^{1/2}}{n^{4/5}} \log \frac{C}{\delta}} + \lambda 4 sB
\label{eqn:second_step_inequality}
\end{align}

@@

\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
   &\leq cB^2 \sigma 
    \sqrt{ \frac{s^5 (b c_u)^{2/5}}{n^{4/5}} \log \frac{C}{\delta}}
 +\lambda 4 s B + c B^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
    \nonumber \\
&\leq c B^3 \sigma \sqrt{ \frac{s^5(bc_u)^{2/5}}{n^{4/5}} \log \frac{2}{\delta}} + \lambda 4 sB
\end{align}

Substituting in $\lambda \leq c sB \sqrt{\frac{1}{n} \log^2 np}$ and we get the desired result.

@@

\begin{proof}
The proof proceeds almost identically to that of theorem~\ref{thm:convex_consistent} because convex and concave functions have the same bracketing number.

@@

Using identical analysis as Step 2 of the proof of Theorem~\ref{thm:convex_consistent} but setting $s=1$, we have, with probability at least $1-\delta$,
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
  c B^2 \sigma \sqrt{ \frac{b^{1/2}}{n^{4/5}} \log \frac{C}{\delta} }+ \lambda 2 Lb
\end{align*}

@@

\begin{lemma}
\label{lem:uniform_convergence}
With probability at least $1-\delta$:
\begin{align*}
\sup_{f \in \mathcal{C}^s_L} \Big| \| f_0 - f \|^2_n - \|f_0 - f \|^2_P\Big| \leq
   c B^2 \sqrt{ \frac{s^5b^{1/2}}{n^{4/5}} \log \frac{2}{\delta}}
\end{align*}

@@

\begin{proof}
Let $\mathcal{G}$ denote the off-centered set of convex functions, that is, $\mathcal{G} \equiv \mathcal{C}^s - f_0$. Note that if $h \in \mathcal{G}$, then $\| h \|_\infty = \| f_0 - f \|_\infty \leq 4 s B$.\\

There exists an $\epsilon$-bracketing of $\mathcal{G}$.

%For every $h \in \mathcal{G}$, there exists $h^L$ in the bracketing such that $\| h^U - h^L \|_{L_1(P)} \leq \epsilon$.

By Corollary~\ref{cor:convexadditive_lp}, the bracketing has size at most $\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**}\left( \frac{2sbB}{\epsilon} \right)^{1/2}$. By Corollary~\ref{cor:convexbracket_ln}, we know that with probability at least $1-\delta$, we have that $\| h_U - h_L \|_{L_1(P_n)} \leq \epsilon + \epsilon_{n,\delta}$ for all pairs $(h_U, h_L)$ in the bracketing, where $\epsilon_{n,\delta} = sB \sqrt{ \frac{K^{**} (2sbB)^{1/2} + \log \frac{1}{\delta}}{2 \epsilon^{1/2} n}}$.

For a particular function $h \in \mathcal{G}$, we can construct $\psi_L \equiv \min( |h_U|, |h_L|)$ and $\psi_U \equiv \max( |h_U|, |h_L| )$ so that
\[
\psi_L^2 \leq h^2 \leq \psi_U^2
\]

We can then bound the $L_1(P)$ norm of $\psi_U^2 - \psi_L^2$.
\begin{align*}
\int (\psi_U^2(x) - \psi_L^2(x)) p(x)dx  &\leq  \int | h_U^2(x) - h_L^2(x)| p(x) dx \\
   &\leq \int | h_U(x) - h_L(x) | \, |h_U(x) + h_L(x)| p(x) dx \\
   &\leq 2sB \epsilon
\end{align*}

% And, with probability at least $1-\delta$, for all $\psi_U, \psi_L$:
% \begin{align*}
% \frac{1}{n} \sum_{i=1}^n ( \psi_U^2(X_i) - \psi_L^2(X_i)) &\leq 
%          \frac{1}{n} \sum_{i=1}^n | h_U^2(X_i) - h_L^2(X_i)| \\
%   &\leq \frac{1}{n}\sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \, |h_U(X_i) + h_L(X_i)| \\
%   &\leq 2sB(\epsilon + \epsilon_{n,\delta})
% \end{align*}

Now we can bound $\| h \|_n^2 - \| h \|_P^2$.

\begin{align}
\frac{1}{n} \sum_{i=1}^n \psi_L(X_i)^2 - \E \psi_U(X)^2  \leq
    \| h \|_n^2 - \| h \|_P^2 \leq
  \frac{1}{n} \sum_{i=1}^n \psi_U(X_i)^2 - \E \psi_L(X)^2  \label{eqn:hpsi_bound}
\end{align}

$\psi_L(X_i)^2$ and $\psi_U(X_i)^2$ are bounded random variables with upper bound $sB$. By uniform convergence, we have that, with probability at least $1-\delta$,, for all $\psi_L$ (and likewise $\psi_U$):
\[
\left| \frac{1}{n} \sum_{i=1}^n \psi_L(X_i)^2 - 
   \E \psi_L(X)^2 \right| \leq (sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} }
\]

Plugging this into equation~\ref{eqn:hpsi_bound} above, we have that:
\begin{align*}
& \E \psi_L(X)^2 - \E \psi_U(X)^2 - 
(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} } \\
 & \leq 
 \| h \|_n^2 - \| h \|_P^2 \leq
\E \psi_U(X)^2 - \E \psi_L(X)^2 + 
(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} }
\end{align*}

Using the $L_1(P)$ norm of $\psi_U^2 - \psi_L^2$ result, we have:
\begin{align*}
-sB\epsilon - 
(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} } \leq 
 \| h \|_n^2 - \| h \|_P^2 \leq
sB\epsilon + 
(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} }
\end{align*}

We balance the terms by choosing $\epsilon = \left( \frac{ (sB)^2 sK^{**} (sBb)^{1/2}}{n} \right)^{2/5}$.

We have then that, with probability at least $1-\delta$,
\begin{align*}
\big| \| h \|_n^2 - \| h \|_P^2  \big| \leq
  B^2 \sqrt{ \frac{s^5 b^{1/2} \log \frac{1}{\delta}}{n^{4/5}}}
\end{align*}

%For a $h \in \mathcal{G}$, let $h_\epsilon$ denote a function in the $\epsilon$-bracketing of $\mathcal{G}$ closest to $h$. It obviously must be that $\| h - h_\epsilon \|_n \leq \| h - h_\epsilon \|_\infty \leq \epsilon$.\\

% Because $\| h \|_n = \| h - h^L + h^L \|_n$, we have that
% \begin{align*}
% \|h^L \|_n - \| h - h^L \|_n &\leq 
%     \| h \|_n \leq \|h^L \|_n + \| h - h^L \|_n \\
% \|h^L \|_n - \epsilon - \epsilon_{n,\delta} &\leq 
%     \| h \|_n \leq \|h^L \|_n + \epsilon + \epsilon_{n,\delta}  \\
% \| h^L \|^2_n - 8 \epsilon (sB)  &\leq \| h  \|^2_n  \leq
%    \| h^L \|_n^2 + 8 \epsilon (sB) 
% \end{align*}
% where we used the fact that $\| h - h^L \|_n \leq \| h - h^L \|_\infty \leq \epsilon$ and $ \| h^L \|_n \leq \| h^L \|_\infty \leq 4 s L b$.

% And likewise:
% \begin{align*}
% \| h_\epsilon \|^2_P - 8 \epsilon (s L b)  &\leq \| h  \|^2_P \leq
%    \| h_\epsilon \|_P^2 + 8 \epsilon (s L b)
% \end{align*}

% Therefore, 
% \begin{align*}
% \sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| \leq 
% \sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
%         + \epsilon (16 sLb)
% \end{align*}

% Since $\| h_\epsilon \|_n^2 = \frac{1}{n} \sum_{i=1}^n h_\epsilon(X_i)^2$ is an average of bounded random variables, we have by Union Bound and Hoeffding Inequality that, with probability at most $1 - \delta$,
% \begin{align*}
% \sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
%   (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
%         + \log N_\infty(\epsilon, \mathcal{C}_L^s) \big) } \\
% &\leq (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
%         + C s^{1.5} Lb \epsilon^{-1/2}   \big) }
% \end{align*}

% We will set $\epsilon = \frac{1}{n^{2/5}} (C s^{0.5} L b)^2$. 
% Therefore:
% \begin{align*}
% \sup_{h_\epsilon} \Big|  \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
%    (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
%         + s n^{1/5}  \big) } \\
%   &\leq (8Lb)^2 \sqrt{ \frac{s^5}{cn^{4/5}} \log \frac{2}{\delta} }
% \end{align*}
% And
% \begin{align*}
% \sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| &\leq 
% \sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
%         + \frac{1}{n^{2/5}} C^2 s^2 (Lb)^3 \\
%   &\leq (8Lb)^2 \sqrt{ \frac{s^5}{c n^{4/5}} \log \frac{2}{\delta}}
%      + (CLb)^2 \sqrt{ \frac{s^4}{n^{4/5}} } \\
%   &\leq c (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
% \end{align*}

@@

\begin{definition}
% upper, lower, epsilon room
% metric
% function space
Let $\mathcal{C}$ be a set of functions. For a given $\epsilon$ and metric $\rho$ (which we take to be $L_2$ or $L_2(P)$), we define a \textbf{bracketing} of $\mathcal{C}$ to be a set of pairs of functions $\{ (f_L, f_U) \}$ satisfying (1) $\rho( f_L, f_U) \leq \epsilon$ and (2) for any $f \in \mathcal{C}$, there exist a pair $(f_L, f_U)$ where $f^U \geq f \geq f^L$.

@@

It is trivial to extend Kim and Samworth's result to $L_2(P)$ norm for an absolutely continuous distribution $P$.

\begin{proposition}
\label{prop:convexbracket_lp}
Let $P$ be a distribution with a density $p$. Let $\mathcal{C}, b, B, \epsilon_3, K^{**}$ be defined as in Proposition~\ref{prop:convexbracket}. Then,
\[
\log N_{[]} (2\epsilon, \mathcal{C}, L_1(P)) \leq K^{**} \left( \frac{2bB}{\epsilon} \right)^{d/2}
\]
For all $\epsilon \in (0, B\epsilon_3]$.
\end{proposition}

\begin{proof}
Let $\mathcal{C}_\epsilon$ be the bracketing the satisfies the size bound in Proposition~\ref{prop:convexbracket_lp}.

Let $(f_L, f_U) \in \mathcal{C}_\epsilon$. Then we have that:
\begin{align*}
\| f_L - f_U \|_{L_1(P)} &= \int | f_L(x) - f_U(x)| p(x) dx \\
   &\leq \left( \int | f_L(x) - f_U(x) |^2 dx \right)^{1/2}
      \left( \int p(x)^2 dx \right)^{1/2} \\
  &\leq \left( \int | f_L(x) - f_U(x)|^2 dx \right)^{1/2}\\
 &\leq \| f_L - f_U \|_{L_2} \leq \epsilon
\end{align*}
On the third line, we used the fact that $\int p(x)^2 dx \leq \left( \int p(x) dx \right)^2 \leq 1$.
\end{proof}

It is also simple to extend the bracketing number result to additive convex functions. As before, let $\mathcal{C}^s$ be the set of additive convex functions with $s$ components.

\begin{corollary}
\label{cor:convexadditive_lp}
Let $P$ be a distribution with a density $p$ upper bounded by $c_u$. Let $b, B, \epsilon_3, K^{**}$ be defined as in Proposition~\ref{prop:convexbracket}. Then,
\[
\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**} 
    \left( \frac{2sbB}{\epsilon} \right)^{1/2}
\]
For all $\epsilon \in (0, s B \epsilon_3]$.
\end{corollary}

\begin{proof}
Let $f \in \mathcal{C}^s$. We can construct an $\epsilon$-bracketing for $f$ through $\epsilon/s$-bracketings for each of the components $\{ f_k \}_{k=1,...,s}$:
\[f_U = \sum_{k=1}^s f_{Uk}  \qquad f_L = \sum_{k=1}^s f_{Lk} \]
It is clear that $f_U \geq f \geq f_L$. It is also clear that $\| f_U - f_L \|_{L_1(P)} \leq \sum_{k=1}^s \| f_{Uk} - f_{Lk} \|_{L_1(P)} \leq \epsilon$.
\end{proof}

The following result follows from Corollary~\ref{prop:convexbracket_lp} directly by an union bound.

\begin{corollary}
\label{cor:convexbracket_ln}
Let $X_1,...,X_n$ be random samples from a distribution $P$. Let $1 > \delta > 0$. Let $\mathcal{C}^s_\epsilon$ be an $\epsilon$-bracketing of $\mathcal{C}^s$ with respect to the $L_1(P)$-norm whose size is at most $N_{[]}( 2\epsilon, \mathcal{C}^s, L_1(P))$. Let $\epsilon \in (0, s B \epsilon_3]$.

Then, with probability at least $1-\delta$, for all pairs $(f_L, f_U) \in \mathcal{C}^s_\epsilon$, we have that

\begin{align*}
\frac{1}{n} \sum_{i=1}^n |f_L(X_i) - f_U(X_i)| &\leq \epsilon + \epsilon_{n, \delta}
\end{align*}

where 
$\epsilon_{n,\delta} \equiv 
sB \sqrt{ \frac{ \log N_{[]}(2\epsilon, \mathcal{C}^s, L_2(P)) + \log \frac{1}{\delta}}{2n}} = 
sB \sqrt{ \frac{sK^{**} (2sbB)^{d/2} + \log \frac{1}{\delta}}{2\epsilon^{d/2} n} }$
\end{corollary}
